Contracts for Contracts

### 2023-04-29 paper/introduction.tex
code style

Solidity does provide first-order assertion primitives (e.g. @require@ or
@modifier@) but they cannot effectively check function values, which are a
common pattern used in smart contract programs.
\zz{
On the other hand, assertion primitives are crucial for ensuring the accuracy and
integrity of a smart contract's business model.
}
\zz{
I'm not sure if this statement applies to the PL community, but from my
understanding, assertions are typically used during testing rather than runtime.
However, in smart contracts, these assertions function as guard conditions and can cause reverts if violated, making them extremely important.
}
Programmers have to manually insert such checks around relevant call-sites, \todo{which is bad}.
%Solidity also provides the @modifier@ mechanism that intercepts
%before and after a function call, thus can be used to check
%pre- and post-conditions.
%\todo{can we compose modifier?}
%\todo{can we attach modifier to callbacks?}
%\todo{can we use modifier to check function's argument?}

@@

\subsubsection*{\textbf{Contracts for Higher-Order Functions}}
Higher-order contracts provides a way to specify and enforce pre- and
post-conditions of untrusted functions. \todo{...}

>>>>

Solidity does provide first-order assertion primitives (e.g. @require@) but
they cannot effectively check function values, which are a common pattern used
in smart contract programs.
\zz{
On the other hand, assertion primitives are crucial for ensuring the accuracy and
integrity of a smart contract's business model.
}
\zz{
I'm not sure if this statement applies to the PL community, but from my
understanding, assertions are typically used during testing rather than runtime.
However, in smart contracts, these assertions function as guard conditions and can cause reverts if violated, making them extremely important.
}
Programmers have to manually insert such checks around relevant call-sites, \todo{which is bad}.
%Solidity also provides the @modifier@ mechanism that intercepts
%before and after a function call, thus can be used to check
%pre- and post-conditions.
%\todo{can we compose modifier?}
%\todo{can we attach modifier to callbacks?}
%\todo{can we use modifier to check function's argument?}

@@

\subsubsection*{\textbf{Contracts for Callable Addresses and Higher-Order Functions}}
Higher-order contracts provides a way to specify and enforce pre- and
post-conditions of untrusted functions. \todo{...}
